### 2013-05-16 Docs/architecture/architecture.tex
some fixes

\maestro\ models problems that are in tight hydrostatic equilibrium.
The fluid state is decomposed into a 1D radial base state that
describes the hydrostatic structure of the star or atmosphere, and a
2- or 3D Cartesian full state, that captures the departures from
hydrostatic equilibrium.  Two basic geometries are allowed.  A {\em
  plane-parallel} geometry assumes that the domain is thin compared to
the radius of curvature of the star, and therefore the 1D base state
is perfectly aligned with the Cartesian state.  A {\em spherical}
geometry is for modeling an entire star.  Here, the 1D base state is
not aligned with the Cartesian state.  Figure~\ref{fig:base_state}
shows these geometries.

@@

The routines in {\tt MAESTRO/initial\_model/} prepare an initial model
for \maestro.  There are two types of routines here, the first type
modify an existing 1D initial model produced somewhere else (e.g.\ a
1D stellar evolution code), and map it onto a uniform grid, at
the desired resolution, using the equation of state in \maestro, and
using \maestro's discretization of hydrostatic equilibrium.  The second
type generate the initial model internally, by integrating the
condition of hydrostatic equilibrium together with a simplifying
assumption on the energy (e.g. isothermal or isentropic).  In
both cases hydrostatic equilibrium is enforced as:
\begin{equation}
\frac{p_{i+1} - p_i}{\Delta r} = \frac{1}{2} (\rho_i + \rho_{i+1})
g_{i+1/2}
\end{equation}
Here, $g_{i+1/2}$ is the edge-centered gravitational acceleration.

@@

>>>>

\maestro\ models problems that are in tight hydrostatic equilibrium.
The fluid state is decomposed into a 1D radial base state that
describes the hydrostatic structure of the star or atmosphere, and a
2- or 3D Cartesian full state, that captures the departures from
hydrostatic equilibrium.  Two basic geometries are allowed.  A {\em
  plane-parallel} geometry assumes that the domain is thin compared to
the radius of curvature of the star, and therefore the 1D base state
is perfectly aligned with the Cartesian state.  A {\em spherical}
geometry is for modeling an entire star\footnote{Spherical geometry
  only exists for 3-d. This is a design decision---convection is 3-d.
  You can however run as an octant}.  Here, the 1D base state is not
aligned with the Cartesian state.  Figure~\ref{fig:base_state} shows
these geometries.

@@

The routines in {\tt AstroDev/initial\_models/}\footnote{The {\tt \astrodev} package is currently distributed separately from \maestro} prepare an initial model
for \maestro.  There are two types of routines here, the first type
modify an existing 1D initial model produced somewhere else (e.g.\ a
1D stellar evolution code), and map it onto a uniform grid, at
the desired resolution, using the equation of state in \maestro, and
using \maestro's discretization of hydrostatic equilibrium.  The second
type generate the initial model internally, by integrating the
condition of hydrostatic equilibrium together with a simplifying
assumption on the energy (e.g. isothermal or isentropic).  In
both cases hydrostatic equilibrium is enforced as:
\begin{equation}
\frac{p_{i+1} - p_i}{\Delta r} = \frac{1}{2} (\rho_i + \rho_{i+1})
g_{i+1/2}
\end{equation}
Here, $g_{i+1/2}$ is the edge-centered gravitational acceleration.

@@

\subsection{Customizing the Initialization}

The best way to customize the initialization (e.g.\ add perturbations)
is to copy from one of the existing problems.  The file {\tt
  initveldata.f90} controls the velocity field initialization and {\tt
  initscaldata.f90} controls the initialization of the scalars
($\rho$, $\rho X_k$, $\rho h$).  The {\tt test2} problem is a good
starting point for plane-parallel and {\tt wdconvect} is a good
starting point for full stars.
